Untitled

### 2023-02-15 Manuscript/Lanuza_et_al_2022.Rmd
adding figure pollinator guilds on trait space to main text and supp. mat.

We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA). We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation. Prior to the analyses, we excluded outliers and standardised the data. Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species. Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012]. Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test. We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010]. Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data. For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.

@@

As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2). Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association. In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7). Regarding self-compatibility, we found larger differences on PC2. For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test *P* \< 0.05). Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test *P* \< 0.05). Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test *P* \< 0.05). Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test *P* \< 0.05). Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test *P* \< 0.05). Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test *P* \< 0.05).

@@

The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns. The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).

@@

Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity. On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c). Again, selectivity showed the opposite trend to the number of visits (figure S9i).

>>>>

We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA). We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, *P* \< 0.01 and Pearson's correlation = 0.36, *P* \< 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation. Prior to the analyses, we excluded outliers and standardised the data. Specifically, due to the high sensitivity of dimensionality reduction to outliers [@serneels2008; @legendre2012], we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species. Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis [@legendre2012]. Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test. Similarly, we also explored for each pollinator guild (see "Visitation patterns" subsection below) the position in the trait space of the plants that interacted with them. We performed the pPCA using the function *phyl.pca* from the package *phytools* [@revell2012] with the method lambda ($\lambda$) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode “covariance” because values for each variables were on the same scale following transformation [@abdi2010]. Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data. For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.

@@

As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2). However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see "Visitation patterns" section below for detailed results from quantitative analyses). Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, *P* \< 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , *P* = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, *P* = 0.23) showed a lack of statistical association. In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8). Regarding self-compatibility, we found larger differences on PC2. For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test *P* \< 0.05). Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test *P* \< 0.05). Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test *P* \< 0.05). Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test *P* \< 0.05). Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test *P* \< 0.05). Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test *P* \< 0.05).

@@

The additional models for the most represented bee families, for both presence-absence of interactions (marginal $R^{2}$ = 0.29; conditional $R^{2}$ = 0.19) and the number of visits (marginal $R^{2}$ = 0.30; conditional $R^{2}$ = 0.03), showed that the Apidae family was the main driver of the observed patterns. The contrast between interaction presence/absence  and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).

@@

Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \~ PCs, conditional $R^{2}$ = 0.11, marginal $R^{2}$ = 0.02; normalised degree \~ PCs, conditional $R^{2}$ = 0.24, marginal $R^{2}$ = 0.02; and, selectivity \~ PCs, conditional $R^{2}$ = 0.37, marginal$R^{2}$ = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity. On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a). However, selectivity (d’) was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g). On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c). Again, selectivity showed the opposite trend to the number of visits (figure S10i).

### 2023-02-15 Manuscript/Lanuza_et_al_2022.tex
adding figure pollinator guilds on trait space to main text and supp. mat.

We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA). We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation. Prior to the analyses, we excluded outliers and standardised the data. Specifically, due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species. Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}). Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test. We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}). Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data. For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.

@@

As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2). Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed a lack of statistical association. In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S7). Regarding self-compatibility, we found larger differences on PC2. For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S7a and figure S7b; Tukey test \emph{P} \textless{} 0.05). Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S7c and figure S7d; Tukey test \emph{P} \textless{} 0.05). Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S7e and figure S7f; Tukey test \emph{P} \textless{} 0.05). Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S7g and figure S7h; Tukey test \emph{P} \textless{} 0.05). Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S7i and figure S7j; Tukey test \emph{P} \textless{} 0.05). Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S7k and figure S7l; Tukey test \emph{P} \textless{} 0.05).

@@

The additional models for the most represented bee families, for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and the number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03), showed that the Apidae family was the main driver of the observed patterns. The contrast between interaction presence/absence and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S8).

@@

Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S9; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, selectivity \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity. On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S9a). However, selectivity (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S9g). On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S9c). Again, selectivity showed the opposite trend to the number of visits (figure S9i).

>>>>

We explored the association between the different quantitative plant traits using a phylogenetically informed Principal Component Analysis (pPCA). We did not include the quantitative variables of flower length and inflorescence width because they were highly and moderately correlated to flower width, respectively (Pearson's correlation = 0.72, \emph{P} \textless{} 0.01 and Pearson's correlation = 0.36, \emph{P} \textless{} 0.01), and thus we avoided overemphasise flower size on the spectrum of trait variation. Prior to the analyses, we excluded outliers and standardised the data. Specifically, due to the high sensitivity of dimensionality reduction to outliers (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}; \protect\hyperlink{ref-serneels2008}{Serneels \& Verdonck, 2008}), we excluded values outside the 2.5th--97.5th percentile range, and thus our final dataset had 1,236 species. Then, we log transformed all continuous variables to reduce the influence of extreme values and then z-transformed (X= 0, SD=1) these variables so that they were within the same numerical range, as recommended for principal component analysis (\protect\hyperlink{ref-legendre2012}{Legendre \& Legendre, 2012}). Although qualitative traits were not included in the dimensionality reduction analysis, we also investigated their position in the trait space and the statistical association of the different qualitative traits with the main axes of trait variation using an ANOVA and Tukey test. Similarly, we also explored for each pollinator guild (see ``Visitation patterns'' subsection below) the position in the trait space of the plants that interacted with them. We performed the pPCA using the function \emph{phyl.pca} from the package \emph{phytools} (\protect\hyperlink{ref-revell2012}{Revell, 2012}) with the method lambda (\(\lambda\)) that calculates the phylogenetic correlation between 0 (phylogenetic independence) and 1 (shared evolutionary history) and we implemented the mode ``covariance'' because values for each variables were on the same scale following transformation (\protect\hyperlink{ref-abdi2010}{Abdi \& Williams, 2010}). Finally, we conducted an additional phylogenetic informed principal component analysis for the subset of species with pollen and nectar quantity data. For this, we included all quantitative traits included in the main pPCA, plus pollen grains and microlitres of nectar per flower.

@@

As expected, due to individual trait correlations between qualitative and quantitative traits (e.g., life form and plant height), we found that most categorical traits were clustered on the trait space and statistically associated with the first two axes of trait variation (figure s2 and table s2). However, the position of plants connected to each of the pollinator guilds was scattered without clear aggregation patterns on the trait space (figure s7; but see ``Visitation patterns'' section below for detailed results from quantitative analyses). Flower symmetry, which was only associated with PC2 (Sum of squares = 8.51, F-value = 14.72, \emph{P} \textless{} 0.01 ), and nectar provision, which was independent of PC1 and PC2 (PC1: Sum of squares = 0.37, F-value = 0.29 , \emph{P} = 0.59; PC2: Sum of squares = 0.83, F-value = 1.43, \emph{P} = 0.23) showed a lack of statistical association. In addition, we found statistical differences between the different categorical trait levels within the trait space (figure S8). Regarding self-compatibility, we found larger differences on PC2. For instance, species with unisexual flowers that were self-incompatible, were statistically differentiated from species with partial or full self-compatibility on this axis (figure S8a and figure S8b; Tukey test \emph{P} \textless{} 0.05). Life forms differed statistically across both axes of trait variation and followed a gradient of larger life forms (trees and shrubs) with lower autonomous selfing to smaller ones (herbs) with higher autonomous selfing (figure S8c and figure S8d; Tukey test \emph{P} \textless{} 0.05). Consequently, lifespan also followed this gradient but perennial and short lived species only differed statistically on PC2 (figure S8e and figure S8f; Tukey test \emph{P} \textless{} 0.05). Species with unisexual flowers (monoecious and dioecious) were clustered on both extremes of the first two principal components and had both the lowest autonomous selfing levels and the highest number of flowers (figure S8g and figure S8h; Tukey test \emph{P} \textless{} 0.05). Moreover, we found that campanulate and capitulum flower shapes were differentiated from tube, papilionaceous, open and brush shapes in the trait space; the former had larger flowers and low autonomous selfing levels, while the latter had more flowers and high autonomous selfing (figure S8i and figure S8j; Tukey test \emph{P} \textless{} 0.05). Finally, in terms of flower symmetry, zygomorphic flowers were associated with high levels of autonomous selfing, whereas actinomorphic flowers were more dependent on pollinators (figure S8k and figure S8l; Tukey test \emph{P} \textless{} 0.05).

@@

The additional models for the most represented bee families, for both presence-absence of interactions (marginal \(R^{2}\) = 0.29; conditional \(R^{2}\) = 0.19) and the number of visits (marginal \(R^{2}\) = 0.30; conditional \(R^{2}\) = 0.03), showed that the Apidae family was the main driver of the observed patterns. The contrast between interaction presence/absence and number of visits for bees on PC1 (figure 3a and figure 3d) was driven by the Andrenidae family, which had more interaction partners but made fewer visits to plant species with few large flowers (figure S9).

@@

Variance within plant species-level network metrics was poorly explained by the three main axes of trait variation (figure S10; number of visits \textasciitilde{} PCs, conditional \(R^{2}\) = 0.11, marginal \(R^{2}\) = 0.02; normalised degree \textasciitilde{} PCs, conditional \(R^{2}\) = 0.24, marginal \(R^{2}\) = 0.02; and, selectivity \textasciitilde{} PCs, conditional \(R^{2}\) = 0.37, marginal\(R^{2}\) = 0.03). Overall, the most notable trends were found on the flower number - flower size axis (PC1) and the style length - autonomous selfing axis (PC3) for number of visits and selectivity. On PC1, the number of visits per flower was higher for plant species with more flowers but was lower for plant species with larger flowers (figure S10a). However, selectivity (d') was higher for plant species with large flowers but lower for plant species with small flowers (figure S10g). On PC3, the number of visits was lower for plants with shorter styles and lower autonomous selfing but higher for plant species with longer styles and higher autonomous selfing (figure S10c). Again, selectivity showed the opposite trend to the number of visits (figure S10i).

### 2023-02-15 Supplementary_Material/Sup_Mat_Lanuza_et_al_2022.Rmd
adding figure pollinator guilds on trait space to main text and supp. mat.

Figures S1 to S9

@@

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig. S7.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species. Categories that differ significantly are denoted with a different letter."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S8.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S9.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics."}

>>>>

Figures S1 to S10

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, out.width="85%",  fig.height=12, fig.width=18,fig.align='center',  fig.cap="\\textbf{Fig. S7.} Location in the trait space of the plants that were visited by each of the different pollinator guilds. The red square indicates that the pollinator guild has been observed in that specific plant. Note that the interactions used to represent the plant-pollinator guild connection are a subset of the total interactions considered in this study as indicated in the Network analysis section (see main text)."}

#Create panel with all plots, qualitative version

library(ggplot2)

#Load plots
bees = readRDS("../Data/RData/Bee_PCA.rds")
coleoptera = readRDS("../Data/RData/Coleoptera_PCA.rds")
lepidoptera = readRDS("../Data/RData/Lepidoptera_PCA.rds")
non_bee_hymenoptera = readRDS("../Data/RData/Non_bee_hymenoptera_PCA.rds")
non_syrphid_diptera = readRDS("../Data/RData/Non_syrphid_diptera_PCA.rds")
syrphids = readRDS("../Data/RData/Syrphids_PCA.rds")

#Make plot
library(patchwork)

bees  + lepidoptera + non_syrphid_diptera + 
coleoptera + non_bee_hymenoptera  + syrphids

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=19, fig.width=13, fig.cap="\\textbf{Fig. S8.} Statistical comparison of the different categories of qualitative traits on the main two axes of trait variation with the full set of species. Categories that differ significantly are denoted with a different letter."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=14, fig.width=27,fig.pos = "!H",fig.cap="\\textbf{Fig. S9.} Interaction (yes/no) and visitation rate of the main bee families on the main axes of trait variation. Fitted posterior estimates of the presence-absence of interaction (plots a, b and c) and visitation rate (plots e, f and g) of Andrenidae, Apidae, Colletidae, Halictidae and Megachilidae across PC1, PC2 and PC3. For visualization purposes, the response variable of number of visits was log-transformed (Y-axis of lower panel)."}

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, results='hide', warning=FALSE, fig.height=18, fig.width=26, fig.cap="\\textbf{Fig. S10.} Association between the main axes of trait variation (showed on different columns) and the distinct plant species level network metrics (showed on different rows). The x-axis shows the most illustrative trait extremes of the trait continuum. Note that the plots are coloured by the different network metrics."}
